% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,
  DIV=11,
  numbers=noendperiod]{scrartcl}
\usepackage{xcolor}
\usepackage[left=15mm,right=15mm,top=20mm,bottom=20mm]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Candara}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\ifLuaTeX
  \usepackage{luacolor}
  \usepackage[soul]{lua-ul}
\else
  \usepackage{soul}
\fi




\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}


\author{}
\date{}
\begin{document}


\subsection*{ANDRÉ LUIZ BARBOSA NUNES DA
CUNHA}\label{andruxe9-luiz-barbosa-nunes-da-cunha}
\addcontentsline{toc}{subsection}{ANDRÉ LUIZ BARBOSA NUNES DA CUNHA}

\textbf{Tenured Assistant Professor of Civil Engineering \textbar{} AI
\& Sustainability in Transport} University of São Paulo
(\href{https://www5.usp.br/en}{USP}) • São Carlos School of Engineering
(\href{https://eesc.usp.br/en/}{EESC}) Department of Transport
Engineering (\href{https://eesc.usp.br/ppgs/stt/}{STT}) • São Carlos,
SP, Brazil

{[}\href{mailto:alcunha@usp.br}{\nolinkurl{alcunha@usp.br}}{]}
\textbar{} +55 16 98119 2339 \textbar{}
\href{https://scholar.google.com.br/citations?user=HI0CQJMAAAAJ&hl=en}{{[}Google
Scholar{]}} \textbar{}
\href{https://orcid.org/0000-0002-0520-0621}{{[}ORCID{]}} \textbar{}
\href{https://www.linkedin.com/in/prof-alcunha/}{{[}LinkedIn{]}}
\textbar{} \href{https://linktr.ee/prof_alcunha}{{[}LinkTree{]}}

\hrulefill

\subsection{PROFESSIONAL SUMMARY}\label{professional-summary}

Tenured civil engineering academic with 12+ years of post-doctoral
experience bridging transport infrastructure, sustainability, and
AI-driven engineering. Research portfolio of \textasciitilde USD 3.38
million in competitive grants and industry contracts. Co-PI on a USD
1.45M FAPESP initiative on pavement recycling and decarbonisation.
Extensive teaching leadership (6 courses, curriculum redesign, inverted
classroom), research supervision (60+ scholars, 3 PhDs and 12 MScs
completed), and institutional governance. International research
experience in Australia, Germany, Croatia, and Portugal.

\hrulefill

\section{EDUCATION}\label{education}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Ph.D.~in Transportation Engineering} \dotfill Nov.~2013\\
  University of São Paulo (USP), São Carlos School of Engineering
  (EESC), Brazil

  \begin{itemize}
  \tightlist
  \item
    \emph{Thesis}:
    ``\texttt{Automatic\ system\ for\ vehicular\ traffic\ parameters\ using\ OpenCV}''
  \item
    \emph{DOI}:
    \href{https://doi.org/10.11606/T.18.2013.tde-19112013-165611}{10.11606/T.18.2013.tde-19112013-165611}
  \item
    Funded by CNPq (National Council for Scientific and Technological
    Development), Brazil.
  \end{itemize}
\item
  \textbf{M.Sc. in Transportation Engineering} \dotfill Oct.~2007\\
  University of São Paulo (USP), São Carlos School of Engineering
  (EESC), Brazil

  \begin{itemize}
  \tightlist
  \item
    \emph{Thesis}:
    ``\texttt{Evaluation\ of\ performance\ measurement\ impact\ on\ truck\ passenger\ car\ equivalents}''
  \item
    \emph{DOI}:
    \href{https://doi.org/10.11606/D.18.2007.tde-27112007-094400}{10.11606/D.18.2007.tde-27112007-094400}
  \item
    Funded by CNPq, Brazil.
  \end{itemize}
\item
  \textbf{B.S. in Civil Engineering} \dotfill Feb.~2004\\
  Federal University of Mato Grosso do Sul (UFMS), Brazil

  \begin{itemize}
  \tightlist
  \item
    \emph{GPA}: 3.79/4.00 \(\rightarrow\) (9.5/10.0), (Highest Honors)
  \end{itemize}
\end{enumerate}

\hrulefill

\section{ACADEMIC APPOINTMENTS}\label{academic-appointments}

\textbf{Tenured Assistant Professor} (equivalent to Associate Professor)
\dotfill 2014 -- present\\
\emph{University of São Paulo (USP), Dept. of Transport Engineering},
São Carlos, Brazil.

\begin{verbatim}
- Director of the Intelligent Transportation Systems (ITS) Research Group.

- Tenure awarded 2021; promoted to Senior Faculty status (MS-3.2).

- Elected: Department Council, Graduate Coordinating Committee (CCP-ET), Center for Educational Technology in Engineering (CETEPE), Research and Innovation Committee (CPqI), Culture & Extension Committee (CCEx)
\end{verbatim}

\textbf{Research Scientist \& Laboratory Specialist} \dotfill 2013 --
2014\\
\emph{University of São Paulo (USP), Department of Transport Engineering
(STT)}, São Carlos, Brazil.

\textbf{Assistant Professor} \dotfill 2010\\
\emph{São Paulo State University (UNESP), College of Engineering of
Bauru (FEB)}, Bauru, Brazil.

\hrulefill

\section{INTERNATIONAL MOBILITY}\label{international-mobility}

\begin{itemize}
\item
  \textbf{University of Melbourne} (Australia) - Visiting Researcher,
  CAPES-Print (2020)
\item
  \textbf{University of Zagreb} (Croatia) - Visiting Lecturer, ERASMUS+
  (2018, 2022)
\item
  \textbf{University of Minho} (Portugal) - Visiting Professor,
  CAPES-FCT (2017)
\item
  \textbf{Technical University of Munich} (Germany) - Visiting
  Professor, FAPESP-BAYLAT (2016, 2017)
\end{itemize}

\subsection{RESEARCH AGENDA - Sustainability \&
Innovation}\label{research-agenda---sustainability-innovation}

\begin{itemize}
\item
  \textbf{Pavement Recycling \& Decarbonization (SDG 9 \& 12)}: Co-PI on
  FAPESP USD 1.45M initiative. Data-driven modelling and optimisation
  for recycled pavement materials; engineering technical protocols for
  net-zero infrastructure.
\item
  \textbf{Urban Climate Resilience \& Social Equity (SDG 11 \& 13)}:
  Assessing multimodal network vulnerability to extreme floods using
  graph theory. Designing fail-safe transport systems for marginalised
  communities.
\item
  \textbf{Next-Gen AI for Global Safety Standards (SDG 3.6)}: Deep
  learning and large multimodal models for real-time traffic anomaly
  detection. Scaling national concessionaire work to global operational
  standards.
\item
  \textbf{Digital Twins \& International Policy (SDG 17)}: Digital twins
  for highway concessions integrating Edge AI and sensor fusion for
  smart city policies.
\end{itemize}

\hrulefill

\section{RESEARCH FUNDING \& GRANTS (\textasciitilde USD 3.38 Million
Total)}\label{research-funding-grants-usd-3.38-million-total}

\emph{Total Funding Secured: \textasciitilde USD 3.38 Million (BRL
18.6M)}

\subsection{Competitive Research Grants
(Peer-Reviewed)}\label{competitive-research-grants-peer-reviewed}

\begin{itemize}
\tightlist
\item
  \textbf{2025--2030:} FAPESP CCD Grant --- ``Pavement Recycling as a
  Pillar of Decarbonisation.'' Co-PI. \textasciitilde USD 1.45M
\item
  \textbf{2023--2028:} FAPESP CEPID ``IARA'' --- AI Recreating
  Environments. Research Collaborator. \textasciitilde USD 1.8M
\item
  \textbf{2023--2026:} CNPq Consolidated Groups --- Traffic modelling
  for smart/connected cities. PI. \textasciitilde USD 13,900
\item
  \textbf{2023--2026:} CNPq Research Productivity --- AI tools for urban
  mobility. PI. \textasciitilde USD 7,200
\item
  \textbf{2021:} Uni. Zagreb --- Innovative Control Strategies for
  Sustainable Mobility. Co-PI. \textasciitilde USD 9,500
\item
  \textbf{2019:} CAPES-Print --- Visiting Professorship, University of
  Melbourne. PI. \textasciitilde AUD 150,000
\item
  \textbf{2018--2022:} CNPq Universal --- Image-based truck axle
  detection and classification. PI. \textasciitilde USD 2,700
\item
  \textbf{2018:} Uni. Zagreb --- Deep learning in intelligent traffic
  control. Co-PI. \textasciitilde USD 10,100
\item
  \textbf{2013--2016:} CAPES/FCT --- Promoting sustainable and safe
  urban mobility. Co-PI. \textasciitilde USD 3,600
\end{itemize}

\subsection{Industry Contracts \& Translational
Research}\label{industry-contracts-translational-research}

\begin{itemize}
\tightlist
\item
  \textbf{2025:} CCR Group (RioSP) --- Redesign truck escape ramp BR-116
  (Via Dutra). PI. \textasciitilde USD 32,700
\item
  \textbf{2023:} CCR Group (RioSP) --- Evaluate truck escape ramp BR-116
  (Via Dutra). PI. \textasciitilde USD 16,300
\item
  \textbf{2019:} ARTERIS (ALS) --- Site optimisation for truck escape
  ramps BR-376. PI. \textasciitilde USD 27,200
\end{itemize}

\hrulefill

\section{RESEARCH SUPERVISION \&
MENTORING}\label{research-supervision-mentoring}

\begin{description}
\tightlist
\item[\textbf{Summary}]
60+ researchers directed. 6 PhD (3 completed, 3 in progress) \textbar{}
15 MSc (12 completed, 3 in progress) \textbar{} 18 scientific initiation
(16 completed) \textbar{} 25 capstone projects completed
\end{description}

\subsection{Completed PhD (3)}\label{completed-phd-3}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \href{}{G.J.M. Oliveira} (2024):
  ``\emph{\href{https://minerva-access.unimelb.edu.au/items/9d41c43a-a211-41ce-92fe-f081fc49e630}{Toward
  a Data-driven Framework to Analyse Temporal and Spatial Distributions
  of Crashes}}''
\item
  \href{https://scholar.google.com/citations?user=AcNWryQAAAAJ&hl=en}{L.A.
  Marcomini} (2025):
  ``\emph{\href{https://doi.org/10.11606/T.18.2025.tde-11022026-082130}{Classification
  of trucks by axles using Deep Learning and a Large Multimodal
  Model}}''
\item
  \href{https://scholar.google.com/citations?user=BqdPZ2gAAAAJ&hl=en}{A.B.
  Morelli} (2025): ``\emph{Analysis of Flood Vulnerability in Brazilian
  Urban Networks Using Graph Theory Tools.}''
\end{enumerate}

\subsection{PhD in Progress}\label{phd-in-progress}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \href{https://scholar.google.com.br/citations?user=0r-M5IcAAAAJ}{E.R.
  Ribeiro}: ``\emph{Analysis of motorcyclist' behaviour on urban
  segments: Relationship between riding patterns and rider profile}''
\item
  \href{https://scholar.google.com.br/citations?user=ietBcOUAAAAJ}{T.V.
  Louro}: ``\emph{Examining The Impacts Of Electric Bicycles On
  Accessibility To Jobs And Spatial Equity}''
\item
  \href{https://scholar.google.com.br/citations?user=hy142eUAAAAJ}{P.H.C.
  Caliari}: ``\emph{Evaluation of causal inference and spatial effects
  on travel behavior}''
\end{enumerate}

\subsection{Completed MSc (12)}\label{completed-msc-12}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \href{}{C.E. Ribeiro} (2024):
  ``\emph{\href{https://doi.org/10.11606/D.18.2024.tde-31102024-114415}{Evaluation
  of deep neural networks for vehicle detection in satellite images}}''
\item
  \href{https://lattes.cnpq.br/6933325479741942}{P.Y. Matsumoto} (2022):
  ``\emph{\href{https://doi.org/10.11606/D.18.2022.tde-18102022-103557}{Calibration
  of Cellular Automata model for simulation of the traffic flow behavior
  in São Paulo roads}}''
\item
  \href{https://lattes.cnpq.br/2263620972100266}{H.S. Stefani} (2021):
  ``\emph{\href{https://doi.org/10.11606/D.18.2021.tde-22082022-091919}{Urban
  roadway traffic flow prediction from crowdsourced speed data}}''
\item
  \href{https://lattes.cnpq.br/7512695029586698}{A.D.Bosco Jr} (2020):
  ``\emph{\href{https://doi.org/10.11606/D.18.2020.tde-18042022-143053}{Usability
  of Points of Interest and network centralities of collaborative maps
  for trip attraction analysis: case study of Curitiba}}''
\item
  \href{https://scholar.google.com.br/citations?user=BqdPZ2gAAAAJ}{A.B.
  Morelli} (2019)
  ``\emph{\href{https://doi.org/10.11606/D.18.2020.tde-13012020-153303}{Exploratory
  analysis of resilience in urban road networks}}''
\item
  \href{https://lattes.cnpq.br/3302815314452867}{B. Kuramoto} (2019):
  ``\emph{\href{https://doi.org/10.11606/D.18.2019.tde-20082019-084513}{Data
  exploration of collaborative maps in evaluations of Brazilian urban
  morphologies}}''
\item
  \href{https://lattes.cnpq.br/1581979506356539}{A.B. Felicio} (2019):
  ``\emph{\href{https://doi.org/10.11606/D.18.2020.tde-12052020-170835}{Evaluation
  of the behavior of motorcyclists through the video image processing
  system}}''
\item
  \href{https://lattes.cnpq.br/3462901770011968}{N.R. Panice} (2018):
  ``\emph{\href{https://doi.org/10.11606/D.18.2018.tde-11122018-213600}{Truck
  axle detection automatic method based on images}}''
\item
  \href{https://lattes.cnpq.br/9374994847060943}{M.M. Thebit} (2018):
  ``\emph{\href{https://doi.org/10.11606/D.18.2018.tde-10122018-225948}{Reconstruction
  of a synthetic O/D matrix using traffic data available on the web}}''
\item
  \href{https://lattes.cnpq.br/3128200022537201}{L.A. Marcomini} (2018):
  ``\emph{\href{https://doi.org/10.11606/D.18.2018.tde-01102018-102649}{Automatic
  identification of traffic behavior using video images}}''
\item
  \href{https://lattes.cnpq.br/1828432370828925}{G.J.M. Oliveira}
  (2018):
  ``\emph{\href{https://doi.org/10.11606/D.18.2018.tde-10092018-150848}{Calibration
  of speed-flow relationship for freeways and multilane highways}}''
\item
  \href{https://lattes.cnpq.br/4988917064689096}{E.R. Ribeiro} (2017):
  ``\emph{\href{https://doi.org/10.11606/D.18.2017.tde-07112017-212156}{Exploratory
  method analysis using Wavelet to detect patterns and anomalies in
  traffic history data}}''
\end{enumerate}

\subsection{MSc in Progress}\label{msc-in-progress}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \href{http://lattes.cnpq.br/7862988333397510}{A.V. Costa}
  ``\emph{Accessibility to Social Services in Belo Horizonte-MG}''
\item
  \href{http://lattes.cnpq.br/6355612958124418}{M.E.S. Michelini}
  ``\emph{Development of an Emission Estimation Model for Brazilian
  Cases}''
\item
  \href{http://lattes.cnpq.br/3660336154224847}{R.O.F.P. Oliveira}
  ``\emph{Urban resilience assessment through a comparative study of
  flood prediction methods}''
\end{enumerate}

\textbf{Alumni Placement}

Graduates placed at national regulatory agencies (ANTT, ARTESP) in
Brazil, leading transport consultancies in Brazil and abroad, and the
financial sector.

\hrulefill

\section{TEACHING PORTFOLIO (USP,
2014-present)}\label{teaching-portfolio-usp-2014-present}

\subsection{Data Science \& Computational
Engineering}\label{data-science-computational-engineering}

\begin{itemize}
\tightlist
\item
  \textbf{Multivariate Data Analysis \& Applied Statistics (Graduate):}
  AI techniques (neural networks, decision trees, genetic algorithms), R
  programming. Students publish from course datasets.
\item
  \textbf{Computational Tools for Civil Engineering (Undergraduate):}
  New elective I designed. 20+ students/year. Spreadsheet programming,
  algorithms, AutoCAD, Civil 3D, GIS.
\end{itemize}

\subsubsection{Core Transport Engineering \&
Simulation}\label{core-transport-engineering-simulation}

\begin{itemize}
\tightlist
\item
  \textbf{Fundamentals of Transportation Engineering (Undergraduate):}
  Inverted classroom, project-based learning, 50+ students. Student
  evaluations: 4.5/5.0.
\item
  \textbf{Traffic Engineering \& Simulation (UG/Graduate):} VISSIM,
  AIMSUN, SUMO, TSIS-CORSIM. Industry-ready skills.
\end{itemize}

\subsubsection{Logistics \& Green
Infrastructure}\label{logistics-green-infrastructure}

\begin{itemize}
\tightlist
\item
  \textbf{Logistics \& Supply Chain Management:} Completely redesigned
  with AI logistics, GIS route planning, Green Logistics.
\item
  \textbf{Airports \& Waterways:} Large compulsory modules, 50+
  students, theory and operational exercises.
\end{itemize}

\subsubsection{Capstone \& Mentorship}\label{capstone-mentorship}

\begin{itemize}
\tightlist
\item
  Supervised 25+ final-year engineering capstone projects and 15+
  internship placements.
\end{itemize}

\hrulefill

\section{PUBLICATIONS}\label{sec-publications}

20 peer-reviewed journal articles \textbar{} 36 refereed conference
proceedings \textbar{} 3 manuscripts under review.

\emph{Students mentored by Prof.~A.L. Cunha are denoted by underlining}.

\subsection{Submitted Manuscripts}\label{submitted-manuscripts}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  SALINAS, K., BARELLA, V., \textbf{CUNHA, A.L.}, \ul{OLIVEIRA, G.M.},
  VIERA, T., NONATO, L.G. (2025) ``ORDENA: ORigin-DEstiNAtion data
  exploration''. \emph{IEEE Transactions on Visualization and Computer
  Graphics}
  \textless{}\href{https://arxiv.org/pdf/2510.18278}{arXiv:2510.18278}\textgreater{}
\item
  \ul{LOURO, T. V.}, GRIGOLON, A. B., \textbf{CUNHA, A. L.}, GEURS, K.
  T. (2025). ``Cycling accessibility and equity: A systematic literature
  review''. \emph{Transport Reviews}.
\item
  \ul{LOURO, T. V.}, TOMASIELLO, D. B., GRIGOLON, A. B., \textbf{CUNHA,
  A. L.}, GEURS, K. T. (2026). ``Integrating e-bikes and bikesharing
  with public transit: Evaluation of impacts on job accessibility and
  spatial equity''. \emph{Journal of Urban Mobility}.
\end{enumerate}

\subsection{Peer-Reviewed Journal}\label{peer-reviewed-journal}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \ul{LOURO, T.V.}; GRIGILON, A.B.; TIRACHINI, A.; \textbf{CUNHA, A.L.};
  GEURS, K.T. (2026) ``How Do E-Bikes Measure Up? Analyzing Speed
  Differences and Network Impacts of São Paulo's Bikesharing System''.
  \emph{Transportation}. DOI:
  \href{https://doi.org/10.1007/s11116-026-10724-y}{10.1007/s11116-026-10724-y}
\item
  \ul{LOURO, T.V.}; GRIGILON, A.B.; \textbf{CUNHA, A.L.}; GEURS, K.T.
  (2025) ``E-bikes' impact on job accessibility and equity in São Paulo
  and Rio''. \emph{Transportation Research Part D}. DOI:
  \href{https://doi.org/10.1016/j.trd.2025.105072}{10.1016/j.trd.2025.105072}
\item
  \ul{DE OLIVEIRA, G.J.M.}; LAVIERI, P.S.; \textbf{CUNHA, A.L.} (2023)
  Integrating a non-gridded space representation into a graph neural
  networks model for citywide short-term crash risk prediction.
  \emph{Urban Informatics}. DOI:
  \href{https://doi.org/10.1007/s44212-023-00032-6}{10.1007/s44212-023-00032-6}
\item
  FLEURY, M.P.; KAMAKURA, G.K.; PITOMBO, C.S.; \textbf{CUNHA, A.L.B.N.};
  FERREIRA, F.B.; LINS DA SILVA, J. (2023) Assessing and Predicting
  Geogrid Reduction Factors after Damage Induced by Dropping Recycled
  Aggregates. \emph{Sustainability}. DOI:
  \href{https://doi.org/10.3390/su15139942}{10.3390/su15139942}
\item
  FLEURY, M.P.; KAMAKURA, G.K.; PITOMBO, C.S.; \textbf{CUNHA, A.L.B.N.};
  LINS DA SILVA, J. (2023) Prediction of non-woven geotextiles'
  reduction factors for damage caused by the drop of backfill materials.
  \emph{Geotextiles and Geomembranes}. DOI:
  \href{https://doi.org/10.1016/j.geotexmem.2023.05.004}{10.1016/j.geotexmem.2023.05.004}
\item
  SILVA, F.A.E.; BESSA JUNIOR, J.E.; COSTA, A.L.; \textbf{CUNHA, A.L.};
  VELHO, D.M.C.; ANDALICIO, A. (2023) Exploratory analysis of the VISSIM
  simulation model for two-lane highways. \emph{Engenharia Civil UM}.
  DOI: \href{https://doi.org/10.21814/ecum.4493}{10.21814/ecum.4493}
\item
  SILVA, F.A.; BESSA JUNIOR, J.E.; COSTA, A.L.; \textbf{CUNHA, A.L.};
  VELHO, D.M.C. (2022) Analysis of no-passing zones to assess the level
  of service on two-lane rural highways in Brazil. \emph{Case Studies on
  Transport Policy}. DOI:
  \href{https://doi.org/10.1016/j.cstp.2021.12.006}{10.1016/j.cstp.2021.12.006}
\item
  \ul{MORELLI, A. B.}; \textbf{CUNHA, A.L.} (2021) Assessing
  vulnerabilities in transport networks: a graph-theoretic approach.
  \emph{Transportes}. DOI:
  \href{https://doi.org/10.14295/transportes.v29i1.2250}{10.14295/transportes.v29i1.2250}
\item
  SILVA, F.A.; BESSA JÚNIOR, J.E.; COSTA, A.L.; \textbf{CUNHA, A.L.};
  ANDALÍCIO, A.F.; DA COSTA VELHO, D.M.; NAZARETH, V.S. (2021)
  Evaluation of the effect of climbing lanes on segments of two-lane
  highways. \emph{Transportes}. DOI:
  \href{https://doi.org/10.14295/transportes.v29i2.2359}{10.14295/transportes.v29i2.2359}
\item
  \ul{MORELLI, A.B.}; \textbf{CUNHA, A.L.} (2021) Measuring urban road
  network vulnerability to extreme events: An application for urban
  floods. \emph{Transportation Research Part D}. DOI:
  \href{https://doi.org/10.1016/j.trd.2021.102770}{10.1016/j.trd.2021.102770}
\item
  MARTINS, D.O.; \ul{OLIVEIRA, G.J.M.}; MORAES, F.R.; SILVA, I.;
  \textbf{CUNHA, A.L.} (2020) Geomatics data management system.
  \emph{Revista Brasileira de Geomática}. DOI:
  \href{https://doi.org/10.3895/rbgeo.v8n1.10141}{10.3895/rbgeo.v8n1.10141}
\item
  PIANUCCI, M.N.; PITOMBO, C.S.; \textbf{CUNHA, A.L.}; LIMA SEGANTINE,
  P.C. (2019) Forecasting household travel demand through a sequential
  method based on synthetic population and artificial neural networks.
  \emph{Transportes}. DOI:
  \href{https://doi.org/10.14295/transportes.v27i4.1409}{10.14295/transportes.v27i4.1409}
\item
  OLIVEIRA, J.V.M.; LAROCCA, A.P.C.; ARAUJO NETO, J.O.; \textbf{CUNHA,
  A.L.}; SANTOS, M.C.; SCHAAL, R.E. (2019) Rigid Bridges Health Dynamic
  Monitoring Using 100 Hz GPS Single-Frequency and Accelerometers.
  \emph{Positioning}. DOI:
  \href{https://doi.org/10.4236/pos.2019.102002}{10.4236/pos.2019.102002}
\item
  DE OLIVEIRA, J.V.M.; LAROCCA, A.P.C.; DE ARAÚJO NETO, J.O.; CUNHA,
  A.L.; DOS SANTOS, M.C.; SCHAAL, R.E. (2019) Vibration monitoring of a
  small concrete bridge using wavelet transforms on GPS data.
  \emph{Journal Of Civil Structural Health Monitoring}. DOI:
  \href{https://doi.org/10.1007/s13349-019-00341-y}{10.1007/s13349-019-00341-y}
\item
  LINDNER, A.; PITOMBO, C.S.; \textbf{CUNHA, A.L.} (2017) Estimating
  motorized travel mode choice using classifiers: An application for
  high-dimensional multicollinear data. \emph{Travel Behaviour and
  Society}. DOI:
  \href{https://doi.org/10.1016/j.tbs.2016.08.003}{10.1016/j.tbs.2016.08.003}
\item
  SOUZA, N.C.; PITOMBO, C.; \textbf{CUNHA, A.L.}; LAROCCA, A.P.C.; DE
  ALMEIDA FILHO, G.S. (2017) Model for classification of linear erosion
  processes along railways through decision tree algorithm and
  geotechnologies. \emph{Boletim de Ciências Geodésicas}. DOI:
  \href{https://doi.org/10.1590/S1982-21702017000100005}{10.1590/S1982-21702017000100005}
\item
  ANDRADE, G.R.; PITOMBO, C.; \textbf{CUNHA, A.L.N.}; SETTI, J.R. (2016)
  A Model for Estimating Free-Flow Speed on Brazilian Expressways.
  \emph{Transportation Research Procedia}. DOI:
  \href{https://doi.org/10.1016/j.trpro.2016.06.032}{10.1016/j.trpro.2016.06.032}
\item
  LAROCCA, A.P.C.; ARAUJO NETO, J.O.; BARBOSA, A.C.B.; TRABANCO, J.L.A.;
  \textbf{CUNHA, A.L.B.N.} (2014) Dynamic Monitoring vertical Deflection
  of Small Concrete Bridge Using Conventional Sensors And 100 Hz GPS
  Receivers - Preliminary Results. \emph{IOSRJEN Journal of
  Engineering}. DOI:
  \href{https://doi.org/10.9790/3021-04920920}{10.9790/3021-04920920}
\item
  \textbf{CUNHA, A.L.}; SETTI, J.R. (2011) Truck equivalence factors for
  divided, multilane highways in Brazil. \emph{Procedia: Social and
  Behavioral Sciences}. DOI:
  \href{https://doi.org/10.1016/j.sbspro.2011.04.447}{10.1016/j.sbspro.2011.04.447}
\end{enumerate}

\subsection{Selected Conference Proceedings (36 total: 10 most recent
shown)}\label{selected-conference-proceedings-36-total-10-most-recent-shown}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \ul{MORELLI, A.B.}; \ul{ALIZON, G.B.}; \textbf{CUNHA, A.L.} (2025)
  Alternative-Route Efficiency in Brazilian Cities: How Flood-Induced
  Collapse Patterns Differ from Random Blockages. In: XXXIX ANPET --
  Research and Teaching in Transport Congress, 2025, Goiânia.
  Proceedings of the 39th ANPET.
\item
  \ul{LOURO, T.V.}; ASSIS, L.B.M.; JUNIOR, J.U.P.; \textbf{CUNHA, A.L.};
  GEURS, K.T (2025) Job Accessibility in the 15-Minute City: A
  Comparative Analysis of Walking, Cycling, and E-Bikes in Four
  Brazilian Cities. In: XXXIX ANPET -- Research and Teaching in
  Transport Congress, 2025, Goiânia. Proceedings of the 39th ANPET.
\item
  ISHIHARA, B.A.; \ul{QUINTINO, P.G.}; \textbf{CUNHA, A.L.}; SETTI, J.R.
  (2025) Operation of Heavy Vehicles on Long, Steep Downgrades: Brake
  Thermal Simulation Based on ABNT NBR 10966-2. In: XXXIX ANPET --
  Research and Teaching in Transport Congress, 2025, Goiânia.
  Proceedings of the 39th ANPET.
\item
  RODRIGUES, L.R.; PITOMBO, C.S.; \textbf{CUNHA, A.L.}; LAROCCA, A.P.C.;
  FERRAZ, A.C.P. (2025) Identification of Crime and Traffic Crash
  Hotspots in the Vicinity of Bus Stops. In: XXXIX ANPET -- Research and
  Teaching in Transport Congress, 2025, Goiânia. Proceedings of the 39th
  ANPET.
\item
  DAVOLI, J.P.; PITOMBO, C.S.; \textbf{CUNHA, A.L.} (2025) Application
  of a Random-Forest--Based Variable Selection Method for the Analysis
  of Post-COVID-19 Active Transportation. In: XXXIX ANPET -- Research
  and Teaching in Transport Congress, 2025, Goiânia. Proceedings of the
  39th ANPET.
\item
  \ul{MORELLI, A.B.}; \textbf{CUNHA, A.L.} (2024) Vulnerability to
  flooding: how long-trip prevalence reduces the efficiency of
  alternative routes. In: XXXVIII ANPET -- Research and Teaching in
  Transport Congress, 2024, Florianópolis. Proceedings of the 38th
  ANPET.
\item
  \ul{MARCOMINI, L.A.}; \textbf{CUNHA, A.L.} (2023) Truck axle detection
  using Neural Networks: analysis of the number of images in the
  training dataset. In: ANPET -- Research and Teaching in Transport
  Congress, 2023, Santos. Proceedings of the 37th ANPET.
\item
  \ul{MORELLI, A.B.}; \ul{LOURO, T.V.}; \textbf{CUNHA, A.L.} (2022)
  Proposal of bikeability indicators from an accessibility perspective:
  identifying roads best suited for cycle lanes using widely available
  data. In: XXXVI ANPET -- Research and Teaching in Transport Congress,
  2022, Fortaleza. Proceedings of the XXXVI ANPET.
\item
  \ul{MORELLI, A.B.}; \textbf{CUNHA, A.L.} (2021) Pedestrian
  accessibility: impacts of morphological and demographic
  characteristics on access to facilities. In: XXXV ANPET -- Research
  and Teaching in Transport Congress, 2021. Proceedings of the XXXV
  ANPET.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \ul{BOSCO JUNIOR, A.D.}; \textbf{CUNHA, A.L.} (2020) Street and zonal
  scale relationship between network centrality and economic activities:
  case study in Curitiba, Brazil. In: PLURIS -- Luso-Brazilian Congress
  on Urban, Regional, Integrated and Sustainable Planning, 2020.
  Proceedings of the 9th PLURIS.
\end{enumerate}

\hrulefill

\section{TECHNICAL PROFICIENCY \& COMPUTATIONAL
STACK}\label{technical-proficiency-computational-stack}

\begin{itemize}
\tightlist
\item
  \textbf{Traffic Simulation:} PTV Vissim, AIMSUN, SUMO, MATSim,
  TSIS-CORSIM (expert: calibration, validation, API scripting)
\item
  \textbf{AI \& Data Science:} PyTorch, TensorFlow, OpenCV, Graph Neural
  Networks, deep learning pipelines
\item
  \textbf{Programming:} Python, R, C++, Julia, SQL, MATLAB, HTML/CSS
\item
  \textbf{Engineering \& GIS:} AutoCAD, Civil 3D, QGIS
\item
  \textbf{E-Learning:} Moodle, Google Classroom, blended/online course
  design, inverted classroom methodology
\end{itemize}

\hrulefill

\section{AWARDS \& HONORS}\label{awards-honors}

\begin{itemize}
\tightlist
\item
  \textbf{ANPET Scientific Production Award} (2023) --- National Agency
  for Transport Research \& Education
\item
  \textbf{Best Professor, Transport Engineering} (2016, 2017) --- USP
  Civil Engineering Academic Secretariat
\item
  \textbf{ABCR Innovation Salon Award} (2015) --- 9th Brazilian Congress
  on Highways \& Concessions
\end{itemize}

\subsection{PROFESSIONAL SERVICES}\label{professional-services}

\subsubsection{University of São
Paulo}\label{university-of-suxe3o-paulo}

\begin{itemize}
\tightlist
\item
  Elected member, Department Council --- faculty hiring, budget,
  strategic partnerships
\item
  Member, Graduate Program Coordinating Committee (CCP-ET) ---
  admissions, curriculum, scholarships
\item
  Member, Research and Innovation Committee (CPqI) --- interdisciplinary
  grants, industry collaboration
\item
  Board member, Center for Educational Technology (CETEPE) ---
  e-learning strategy
\item
  Member, Culture \& Extension Committee (CCEx) --- pedagogical
  modernisation
\end{itemize}

\subsubsection{Editorial \& Peer Review}\label{editorial-peer-review}

\begin{itemize}
\tightlist
\item
  Reviewer: \emph{Transportation Research Part E}, \emph{Engineering
  Applications of AI (EAAI)}, \emph{Sustainable Cities and Society}
\item
  Technical Committees: Transportation Research Board (TRB), IEEE ITSS,
  ANPET
\end{itemize}

\subsubsection{Industry Engagement}\label{industry-engagement}

\begin{itemize}
\tightlist
\item
  CCR Group \& ARTERIS --- national safety standards for truck escape
  ramps on Brazilian federal highways
\item
  TECTRAN --- Minas Gerais State Logistics Plan (PELT)
\item
  Media: research featured on Rede Globo's \emph{Jornal Hoje} (national
  broadcast)
\end{itemize}




\end{document}
